### 2018-12-17 README.Rmd
small changes preparing for initial pre-CRAN release

Areal interpolation is the process making estimates about the population features from a source set of polygons to an overlapping but incongruent set of target polygons. One challenge with areal interpolation is that, while the processes themselves are well documented, implementing them often involves "reinventing the wheel." Within `R`, the `sf` package does offer a basic interface for areal weighted interpolation (`st_interpolate_aw`). The `areal` package is designed to provide a suite of interpolation functions that provide a more full-featured workflow that fits into both modern data management (e.g. `tidyverse`) and spatial data (e.g. `sf`) frameworks.

>>>>

Areal interpolation is the process making estimates about the population features from a source set of polygons to an overlapping but incongruent set of target polygons. One challenge with areal interpolation is that, while the processes themselves are well documented, implementing them often involves "reinventing the wheel." Within `R`, the `sf` package does offer a basic interface for areal weighted interpolation (`st_interpolate_aw`). The `areal` package contains a suite tools for validation and estimation, providing a full-featured workflow that fits into both modern data management (e.g. `tidyverse`) and spatial data (e.g. `sf`) frameworks.
